Weekday sleep, total cholestrol and the modifying effect of age on systolic blood pressure: An analysis of the 2015-2018 non-obese NHANES population

### 2023-12-11 manuscript/paper.Rmd
update

All models fitted to the data in this investigation were nested and evaluations were based on information criteria including Akaike Information Criteria (AIC) and Bayesian Information Criteria (BIC). [BIC] Additionally, we also used performance measures including the mean squared error (MSE), r-squared, and adjusted r-squared. The likelihood ratio test (LRT) was used in competing model comparisons testing the null hypothesis that the nested models are equivalent, and the extra parameters in the larger model do not improve the fit significantly, that is, these terms have effect sizes equivalent to 0. \@ref(tab:tabmodel) summarizes the model performance metrics compared for all models implemented in this investigation.

Here is where we add something....

## compare model 5 with model 2 because they have competing BIC and Adj R^2

>>>>

All models fitted to the data in this investigation were nested and evaluations were based on information criteria including Akaike Information Criteria (AIC) and Bayesian Information Criteria (BIC). Additionally, we also used performance measures including the mean squared error (MSE), r-squared, and adjusted r-squared. The likelihood ratio test (LRT) was used in competing model comparisons testing the null hypothesis that the nested models are equivalent, and the extra parameters in the larger model do not improve the fit significantly, that is, these terms have effect sizes equivalent to 0. \@ref(tab:tabmodel) summarizes the model performance metrics compared for all models implemented in this investigation.
